% Specify the type of document
\documentclass[10pt]{article}

% Load a number of useful packages
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
 \usepackage[margin=1.0in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}

\usepackage{listings}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}


\lstset{language=Matlab,%
    %basicstyle=\color{red},
    breaklines=true,%
    morekeywords={matlab2tikz},
    keywordstyle=\color{blue},%
    morekeywords=[2]{1}, keywordstyle=[2]{\color{black}},
    identifierstyle=\color{black},%
    stringstyle=\color{mylilas},
    commentstyle=\color{mygreen},%
    showstringspaces=false,%without this there will be a symbol in the places where there is a space
    numbers=left,%
    numberstyle={\tiny \color{black}},% size of the numbers
    numbersep=9pt, % this defines how far the numbers are from the text
    emph=[1]{for,end,break},emphstyle=[1]\color{red}, %some words to emphasise
    %emph=[2]{word1,word2}, emphstyle=[2]{style},    
}

\newcommand\scalemath[2]{\scalebox{#1}{\mbox{\ensuremath{\displaystyle #2}}}}


% Say where pictures (if any) will be placed
\graphicspath{{./pictures/}}

% Define title, author, and date
\title{OUFTI 1 \& OUFTI 2 \\
  \large Attitude Determination and Control System}
\author{Emilio R. Gordon}
\date{March 13, 2018}


% Start of document
\begin{document}
% Put the title, author, and date at top of first page
\maketitle

\tableofcontents
\newpage
\section{Introduction }
In 2016, The university of Liege developed the first nanosatellites ever made in
Belgium : OUFTI-1 and OUFTI-2. The satellite is led by students supported by
professors much like our University's SatDev program. OUFTI-1 is a 1U cubesat and is
the first satellite equipped with the amateur radio digital-communication
protocol: the D-STAR technology. Other experiments that will be aboard OUFTI-1 are an
innovative electrical power system as well as high-performance solar cells. The satellite is
not required to point in one specic direction and the Attitude Determination and Control
System (ADCS) subsystem relies on Passive Magnetic Attitude Stabilization (PMAS). The
rst part of this thesis presents this design made of a permanent magnet and hysteretic bars.
The magnet orients the satellite along the Earth's magnetic eld lines and the hysteretic
bars damp its rotational velocities. The inuence of the magnet on the hysteretic bars as
well as the nite elongation of the bars are carefully studied.
OUFTI-2 is the next satellite in the series. Its size is planned to be twice the size of
OUFTI-1 and its main payload will be a radiometer to perform a direct measurement
of the net heating of the Earth. The radiometer is developed in cooperation with the
Royal Meteorological Institute of Belgium and is called Sun-earth IMBAlance (SIMBA)
radiometer. The second part of this master thesis focuses on the feasibility study of an
active attitude control system which satises the requirements of the payload.
\subsection{The OUFTI family}
\subsection{OUFTI-1}
\subsection{OUFTI-2}
\subsection{Attitude Determination and Control System}
\subsubsection{Passive attitude control and OUFTI-1}
\subsubsection{Active attitude control and OUFTI-2}
\section{Mathematical modelling and Coordinate systems}
\section{Passive ADCS of OUFTI-1}
\subsection{Attitude determination of OUFTI-1}
\section{Active Control for Oufti-2}
\subsection{Payload, orbit and requirements}
\subsection{Attitude determination}
\subsubsection{Sun sensors}
\subsubsection{Magnetometers}
\subsubsection{Gyroscopes}
\subsubsection{Star sensors}
\subsection{Attitude control}
\subsubsection{Magnetic torquers}
\subsubsection{Momentum exchange devices}
\subsubsection{Thrusters}
\subsection{Existing hardware for active control }
\subsection{Conclusion}
\section{Simulations of an active attitude control}
\subsection{Application of quaternions to active control}
\subsection{Attitude determination}
\subsection{Torque free motion}
\subsection{Attitude control models}
\subsection{General parameters for the active control simulations}
\subsection{PID controller}
\subsection{The linear quadratic regulator controller}
\subsection{Detumbling controller based on B-dot}
\subsection{Attitude model with full controllability}
\subsection{Attitude model with only magnetic torquers}
\subsubsection{Magnetic torquers with one reaction wheel}
\section{Conclusions}
\subsection{OUFTI-1}
\subsection{OUFTI-2}
\end{document}